Meta-analytic findings of the self-controlled motor learning literature: Underpowered, biased, and lacking evidential value

### 2021-08-12 docs/manuscript.tex
update: match Meta-Psych original submission and restructure repo

\author{Brad McKay\textsuperscript{1}, Zachary D. Yantha\textsuperscript{1}, Julia Hussien\textsuperscript{1}, Michael J. Carter\textsuperscript{2}, and Diane M. Ste-Marie\textsuperscript{1}}

\affiliation{\vspace*{18pt}\textsuperscript{1}\emph{School of Human Kinetics, University of Ottawa} \\
			 \textsuperscript{2}\emph{Department of Kinesiology, McMaster University}}

@@

\authornote{
  \addORCIDlink{Brad McKay}{0000-0002-7408-2323}

  \addORCIDlink{Zachary D. Yantha}{0000-0003-1851-7609}

  \addORCIDlink{Julia Hussien}{0000-0001-7434-228X}

  \addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}

  \addORCIDlink{Diane M. Ste-Marie}{0000-0002-4574-9539}

Correspondence concerning this article should be addressed to Brad McKay. E-mail: \href{mailto:bradmckay8@gmail.com}{bradmckay8@gmail.com}
}

@@

Wulf et al.           & 2015 (Exp 1)    & Lab-Applied & No           & Repetition schedule   & Adult        & 24-hr              & 68  & Yes       \\

>>>>

\author{Brad McKay\textsuperscript{1}, Zachary D. Yantha\textsuperscript{1}, Julia Hussien\textsuperscript{1}, Michael J. Carter\textsuperscript{2}, Diane M. Ste-Marie\textsuperscript{1}}

\affiliation{\vspace*{18pt}\textsuperscript{1}\emph{University of Ottawa} \textsuperscript{2}\emph{McMaster University}}

@@

\authornote{Submitted to \emph{Meta-Psychology}. Participate in open peer review by commenting through \href{hypothes.is}{hypothes.is} directly on this preprint. The full editorial process of all articles under review at \emph{Meta-Psychology} can be found here: \href{https://tinyurl.com/mp-submissions}{https://tinyurl.com/mp-submissions} \newline
You will find this preprint by searching for the first authors name.

  \addORCIDlink{Brad McKay}{0000-0002-7408-2323} \newline
  \hangindent=1.3cm \addORCIDlink{Zachary D. Yantha}{0000-0003-1851-7609} \newline
  \hangindent=1.3cm \addORCIDlink{Julia Hussien}{0000-0001-7434-228X} \newline  
  \hangindent=1.3cm \addORCIDlink{Michael J. Carter}{0000-0002-0675-4271} \newline 
  \hangindent=1.3cm \addORCIDlink{Diane M. Ste-Marie}{0000-0002-4574-9539}

Author correspondence: Brad McKay at \href{mailto:bradmckay8@gmail.com}{bradmckay8@gmail.com}
}

@@

Wulf et al.           & 2015, Exp 1    & Lab-Applied & No           & Repetition schedule   & Adult        & 24-hr              & 68  & Yes       \\
